Volatility Metric to Detect Anomalies in Source Code Repositories

### 2020-04-19 paper/article.tex
more

Yet another simple metrict from the family is
the number of changes being made to a particular file, class, method
or line of code is yet another simple metric, used for example by~\citet{demeyer2000}
in order to analyze the effect of refactorings.

@@

To our knowledge, the metrics introduced in this research, in order
to detect anomalies in source code repository maintenance, has never been
suggested.

@@

>>>>

Yet another simple metric from the family is
the number of changes being made to a particular file, class, method
or line of code, which is used for example by~\citet{demeyer2000}
in order to analyze the effect of refactorings.

@@

To our knowledge, the metrics introduced in this research in order
to detect anomalies in source code repository maintenance, has never been
suggested.

@@

It would be beneficial in future researches to analyze the relationship between
volatility and other parameters of source code repositories,
such as
the programming language being used,
the popularity in GitHub (the number of stars and forks),
the total number of lines of code,
the average number of lines of code per file,
the number of Git commit authors,
the total age of the repository,
the number of issues and pull requests in GitHub,
and many others.
Would be interesting to empiricially demonstrate which of these parameters
(or combinations of them)
impact the behavior of volatility and in which direction.
